A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-16 mt-marathon.2013/PBML_article.tex
changes

Statistical machine translation is a dynamic field which is constantly evolving. A major challenge for the Moses project, in common with many long-term software projects, is to maintain and update the the underlying framework and infrastructure to enable this evolution to continue.

>>>>

Statistical machine translation is a dynamic field which is constantly evolving. A major challenge for the Moses project, in common with many long-term software projects, is to maintain and update the the underlying framework and infrastructure to enable this evolution to continue. The paper documents the major changes that were made to Moses to enable this to happen and compare it two other decoders which implements the same decoding formalism.

Even though each decoder was created independently, their output are comparable. We see that be doing an indepth analysis of the working of each decoder and comparing their model score, we are able to transfer the best optmization technique from each decoder to the others.
